Exploratory Plots

### 2020-09-14 exploratory/2020/sub3_fit_subsets.Rmd
Show open & closed performance on one plot

```{r fit_ref_frac_open}
sensspec_fit %>%
  filter(method == 'open') %>% 
  group_by(dataset, ref_weight) %>%
  ggplot(aes(x = as.factor(ref_frac), y = mcc, color = dataset)) +
  geom_boxplot() +
  scale_color_manual(values = dataset_colors) +
  ylim(0.5, 1) +
  facet_grid(dataset ~ ref_weight) +
  labs(title='Open-reference OptiFit Performance',
       x='reference fraction')
```

```{r fit_ref_frac_closed}
sensspec_fit %>%
  filter(method == 'closed') %>% 
  group_by(dataset, ref_weight) %>%
  ggplot(aes(x = as.factor(ref_frac), y = mcc, color = dataset)) +
  geom_boxplot() +
  scale_color_manual(values = dataset_colors) +
  ylim(0.5, 1) +
  facet_grid(dataset ~ ref_weight) +
  labs(title='Closed-reference OptiFit Performance',
       x='reference fraction')
```

>>>>

```{r fit_ref_frac}
sensspec_fit %>%
  ggplot(aes(x = as.factor(ref_frac), y = mcc, color = dataset)) +
  geom_boxplot() +
  scale_color_manual(values = dataset_colors) +
  ylim(0.5, 1) +
  facet_grid(method ~ ref_weight) +
  labs(title='OptiFit Performance',
       x='reference fraction')
```
